---
title: "Stupid Shiny Presentation for Stupid Shiny APP"
author: "César Arquero Cabral"
date: "14 de febrero de 2019"
output:
  ioslides_presentation:
    widescreen: true
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = F, message = F, tidy=T, warning = F)
```

## Intructions
Here you will find easy instructions to use the marvellous **Stupid Shiny APP**.

### Data source
Each time you call the APP it downloads a bunch of tweets with the function *search_tweets()*. You just need to select a word as a filter, a number of tweets the APP is going to download and apply changes.

### Goals
The APP contain 3 tabs showing the following:
1. A boxplot of number of words by source. Something very very useful to be an autentic data analyzer.
2. A map showing just those tweets geolocated. I mean, as we must know, twitter captures all geolocations, that's for sure, but, data contain just those coords autorized by users...I guess.
3. A render table of just one column: tweets. 
Moreover, there is an extra plot comparing the number of followers by group.

## Process 1: libraries and data
Libraries will be not in **ui.R** or **server.R** but in another file called **Base.R**. The following code allows you to load libraries and install them in case ther are not already installed in the system.
```{r,  eval=F, echo=T, tidy =TRUE}
libraries <- c("processx", "devtools", "ROAuth", "jsonlite", "rtweet", "ggplot2",
               "dplyr", "stringi", "tidytext", "leaflet", "yaml", "digest", "udunits2", 
               "wordcloud", "wordcloud2", "topicmodels", "ngram", "Rmpfr", "stringr","shinyjs",
               "base64enc","httpuv", "plotly", "data.table")

lapply(libraries, function (x) {if(x %in% rownames(installed.packages()) == FALSE) {install.packages(x)}})
lapply(libraries, require,  character.only=T)
```

## ui.R document
Here is the code structure for the **ui.R** document that defines *what you see* in this APP.
```{r, eval=F, echo=T, tidy =TRUE}
fluidPage(
    headerPanel("Stupid Shiny APP - Useless word analysis"),
    sidebarLayout(
        sidebarPanel(helpText("This is an Stupid shinny app that allows you to make useless 
                              word analysis from words found in twitter. 
                              Follow the steps:"),
                     helpText("(1) Pick a word"),
                     helpText("(2) Define the number of tweets you want to analyze"),
                     helpText("(3) Push the button and enjoy the USELESS"),
                     
                     textInput(inputId = "UserOrHashtag",
                               label = "Twitter User or Hashtag:",
                               value = "Roma"),
                     sliderInput("Ntweets", "Maximum number of tweets to capture:",
                                 min=250, max= 5000, value=500, step = 1),
                     submitButton("Update View", icon = icon("refresh")),
                     width = 3),
        mainPanel(
            tabsetPanel(
                tabPanel("Boxplot de kk",plotlyOutput("P1")),
                tabPanel("Miermap",leafletOutput("M1")),
                tabPanel("Tweets and go home",tableOutput("T1"))
            ))))
```

## server.R document
Here is the code structure for the **ui.R** document that defines *what you see* in this APP.
Code has been collapsed and reduced (hard to read) in order to fit the slide length. Most of the complete code is based on a previous exercise [Stupid MAP](http://rpubs.com/cesarkero/430537).
```{r, eval=F, echo=T, tidy =TRUE}
shinyServer(function (input, output) {
    tweets <- reactive ({
        tweets <- search_tweets(q=input$UserOrHashtag,n=input$Ntweets,include_rts = F) #capture tweets based on inputs
    PLOT1 <- reactive({ # create plot and filter sources before
        t <- tweets()
        #...here t must be prepared to be plotted...
        PLOT1 <- plot_ly(t, y = ~Nwords, type="box", color = ~factor(source))})
    MAP1 <- reactive({ # create map
        if (#there is any tweets with coords...) { ## points to be mapped
            MAP1 <- tweet_coords %>% leaflet(width="100%") %>% addTiles(group="OSM") #simple map
        } else {
            #data preparation (based on Stupid_MAP)
            #MAP
            MAP1 <- tweet_coords %>% leaflet(width="100%") %>% addTiles(group="OSM") %>%
                # add base groups, marks, layers, etc
        }})
    TABLE1 <- reactive({TABLE1 <- tweets()$text}) # create table
    #OUTPUTS
    output$P1 <- renderPlotly({PLOT1()})
    output$M1 <- renderLeaflet({MAP1()})
    output$T1 <- renderTable({TABLE1()})
})
```
## Conclusion


No brain = No discussion. No discussion = No conclusion.

Have a nice day and don't be stupid.
